---
title: "Syllabus"
author: Giuliano Colosimo
date: "`r Sys.Date()`"
bibliography: /Users/giulianocolosimo/Dropbox/manuscripts/literature/bibtex/comprehensive_database.bib
csl: /Users/giulianocolosimo/Dropbox/manuscripts/literature/bibtex/apa_5th_edition.csl
citation_package: biblatex
citecolor: "red"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```


## General information

This is a course for master level students enrolled in the "Biologia Evoluzionistica, Ecologia e Antropologia Applicata" degree at the University of Rome Tor Vergata. It is worth **6 CFU** for a total of 48 hours to be administered in person (or remotely, depending on the evolution of the pandemic) during the second semester of academic year 2022/2023. Below is the tentative schedule for each class.


|                      | Day       | Time           | Location                |
|----------------------|-----------|----------------|-------------------------|
| Lectures             | Tue & Thu | 09:00 - 11:00  | AULA Centro Studi Pesca |
| Mid term exam - 1    | 18 April 2023       | 09:00 - 11:00 | AULA Centro Studi Pesca |
| Mid term exam - 2    | 25 May 2023       | 09:00 - 11:00 | AULA Centro Studi Pesca |
| Final exam           | TBD       | 09:00 - 11:00 | AULA Centro Studi Pesca |


::: callout-important
Attendance is mandatory!!
:::


```{r aula, echo=FALSE}
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng = 12.62825, lat = 41.85024, popup="AULA Centro Studi Pesca")
```


## Course language

The course will be thought in Italian unless international students are present. In this latter case the course will be thought in English. All the material and the literature used (including this website!) will be in English.

## Pre-requisites

Students participating to this class should have a good knowledge of zoology, ecology, population biology,  genetics, and molecular biology.

## Textbook

There is no mandatory textbook to buy. All students are required to attend classes and take notes during lessons. The material covered in class will be complemented by the scientific literature provided by the professor. 

## Additional Resources

If you are interested in buying something to deepen your studies some good books are:

- Introduction to conservation genetics [@Frankham2010]
- Conservation Biology [@VanDyke2020]
- Conservation and the Genomics of Populations [@Allendorf2022]

## Learning objectives

The course aims at providing students with an overview of the problems, techniques of analysis and identification of solutions related to conservation of Biodiversity, especially at the level of population and species. By discussing the genetic basis of adaptation, the relationship between population size and evolutionary potential, and population biology, the student develops autonomy in the process of understanding of different approaches and methods, consolidating the awareness that conservation biology is a crisis discipline that requires specific analytical skills to guide appropriate interventions.

Students will develop professional language and communication skills through a continuous interaction with the teacher and interventions during classes. Additionally, students are guided in the understanding of the discipline through the access to primary literature in English. The process of development such skills is monitored by written periodical checks, with open questions.

## Class evaluation

There will be 2 mid-term exams (see schedule page for the dates). All students have to take the midterm exams. At the end of the course, after the second mid term the student can choose to keep the grade and record it or disregard it and try for a better grade in the final written evaluation.

## Meeting hours

Each student is welcome and encouraged to contact me by e-mail with questions and doubts. My office hours are between 10:00 and 12:00 every Wednesday. My office is number 14, located on the first floor of the main building at "Laboratori di Ecologia Sperimentale ed Acquacoltura". 


```{r ufficio, echo=FALSE}
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng = 12.6298, lat = 41.85021, popup="Office 14 is located on the first floor of this building")
```


::: callout-tip
It is always a good idea to e-mail me before coming to the office, to prevent overcrowding.
:::

## Students with disabilities

Please, let me know if you require special accommodations to follow this class.

## Diversity, Equity, and Inclusion

The success of this class depends on all of us creating a safe environment where students feel comfortable sharing their thoughts and opinions. We should all strive to be respectful and supportive of one another during class discussions. Conservation biology is an evolving field and is made better by the contribution of diverse perspectives, and I hope that our class conversations can reflect that.

# References